\section{Reports}
The \emph{Reports} tab is still in ALPHA stage.

To create a report, you need to select a table or view from which the data will be retrieved.  Tables are recommended for those with slow connections to their database, ie. over the internet.

After selecting the data source, the column names will be retrieved and referred to as \emph{fields} in the listbox designated for this purpose.  When you click on a field name, it will be displayed in the report canvas.  Clicking and dragging on the field name in the canvas allows you to move it and also modify its properties: font, justification, etc.

Here's what's being worked on for the reports module:

DONE:
\begin{itemize}
\item Allows for reports based on tables or views.
\item Formulas are just Tcl evals, where column names are available as variables.
  Try: concat \$colname1 \$colname2
  Formulas can also be functions, but must begin with \emph{Function::}
  Try: Function::get\_my\_function(\$colname1,\$colname2)
\item Pictures must be gif or bmp files (and not stored in the database).
\item Page header is the first record on a page, page footer is the last.
\item Detail group is all the records that can fit on a page, row by row.
\item Multiple pages.
\item Printing puts the report into a Postscript file.
  The pages printed are the ones in and between the boxes on preview mode.
  You can also pipe the output by entering it in the dialog when prompted.
  Try: |lpr
  (This is the default if you go to print and don't enter a file name.)
\item Page resizing can be done by typing in the Page size boxes.
\item Report resizing can be done by typing in the Report size boxes and hitting
enter or dragging the window and clicking in it with the mouse.
\item Putting detail groups into columns when the page is wider than the report.
\end{itemize}

DOING:
\begin{itemize}
\item Allow for reports based on queries.
\item Report headers and footers.
\item Grouping and sorting based on database columns (aka fields).
  The GUI is done, but the logic needs work.
\item Subtotals.
\item Drawing simple shapes like lines or circles.
\item Font choice needs expanding.
\item Postscript gets huge when you include pictures.  Maybe include a picture's data only once per report.
\end{itemize}
